Think again?\\ The amount of mental simulation tracks uncertainty in the outcome

### 2015-04-30 manuscript.tex
More clarification

\begin{table}
    \centering
    \begin{tabular}{ccl}
    \toprule
    \textbf{Model} & \textbf{Bounces} & \textbf{Correlation} \\
    \midrule
    $T=1$ & 0   & \NoSamplesHoleRTCorrZeroBounces{} \\
          & 1   & \NoSamplesHoleRTCorrOneBounce{} \\
          & 2   & \NoSamplesHoleRTCorrTwoBounces{} \\
          & all & \NoSamplesHoleRTCorr{} \\
    \midrule
    $T=2$ & 0   & \HoleRTCorrZeroBounces{} \\
          & 1   & \HoleRTCorrOneBounce{} \\
          & 2   & \HoleRTCorrTwoBounces{} \\
          & all & \HoleRTCorr{} \\
    \bottomrule
    \end{tabular}
    \vspace{.25cm}
    \caption{\textbf{Correlations between human and model RTs.} The SPRT model ($T=2$) can capture variations in RTs within bounce conditions, while the single sample model ($T=1$) cannot. Note that the correlations for the $T=1$ model are non-zero because we estimate $\mathbb{E}[B]$ from the simulation model, so there is some variation in the expected number of bounces across stimuli.}
    \label{tbl:rt}
\end{table}

>>>>

\begin{table}
    \centering
    \begin{tabular}{ccl}
    \toprule
    \textbf{Model} & \textbf{Bounces} & \textbf{Correlation} \\
    \midrule
    $T=1$ & 0   & \NoSamplesHoleRTCorrZeroBounces{} \\
          & 1   & \NoSamplesHoleRTCorrOneBounce{} \\
          & 2   & \NoSamplesHoleRTCorrTwoBounces{} \\
          & all & \NoSamplesHoleRTCorr{} \\
    \midrule
    $T=2$ & 0   & \HoleRTCorrZeroBounces{} \\
          & 1   & \HoleRTCorrOneBounce{} \\
          & 2   & \HoleRTCorrTwoBounces{} \\
          & all & \HoleRTCorr{} \\
    \bottomrule
    \end{tabular}
    \vspace{.25cm}
    \caption{\textbf{Correlations between human and model RTs.} The SPRT model ($T=2$) can capture variations in RTs within bounce conditions, while the single sample model ($T=1$) cannot. To compute the correlations within bounce conditions, we grouped stimuli by the number of bounces shown in the feedback, but within bounce conditions we estimate $\mathbb{E}[B]$ from the simulation model. Thus, the expected number of bounces varies slightly across stimuli, which is why the correlations for the $T=1$ model are non-zero.}
    \label{tbl:rt}
\end{table}
